Spatial Reasoning and Statistical Graphics

### 2014-10-11 Paper/Draft1/TestingVisualAptitude.Rnw
Comment clarification for scaling
Remove "value" X label

\comment{\textit{So are we scaling things by the variance/std dev. under random guessing? Or by the theoretical test range?}}

@@

qplot(data=lineup.summary.categorical, x=value, y=lineup, geom="boxplot") + facet_wrap(~variable, scales="free_x") + xlab("Value") + ylab("Lineup Score (# Correct - 1/19 # Incorrect)") + theme_bw() + geom_point(aes(x=value, y=lineup), shape=1, size=3)
ggsave(paste(imgdir, "fig-VisReasoningAnalysisCat.png", sep=""), width=6, height=6)
@

>>>>

\comment{\textit{So are we scaling things by the variance/std dev. under random guessing? Or by the theoretical test range?}\\
Right now, I'm assuming that we're scaling between 0 and 100 by test range $[-a, b]$. So we take the guessing-fixed score and add $a$, then divide by $(a+b)$ and multiply by 100.}

@@

qplot(data=lineup.summary.categorical, x=value, y=lineup, geom="boxplot") + facet_wrap(~variable, scales="free_x") + xlab("") + ylab("Lineup Score (# Correct - 1/19 # Incorrect)") + theme_bw() + geom_point(aes(x=value, y=lineup), shape=1, size=3)
ggsave(paste(imgdir, "fig-VisReasoningAnalysisCat.png", sep=""), width=8, height=6)
@
